%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Medium Length Professional CV
% LaTeX Template
% Version 2.0 (8/5/13)
%
%
% Important note:
% This template requires the resume.cls file to be in the same directory as the
% .tex file. The resume.cls file provides the resume style used for structuring the
% document.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass{resume} % Use the custom resume.cls style

\hyphenpenalty 5000
\usepackage[left=0.5in,top=0.3in,right=0.5in,bottom=0.2in]{geometry} % Document margins
\newcommand{\tab}[1]{\hspace{.2667\textwidth}\rlap{#1}}
\newcommand{\itab}[1]{\hspace{0em}\rlap{#1}}
\name{HAOMING JIN} % Your name
%\address{
%Address: 3000 SW 35th PL, Apt B301, Gainesville, FL, 32608} % Your address
%Address: 2283 Hearst Ave, Apt 18, Berkeley, CA, 94709} % Your address
%Address: 65 Hemlock Circle, Princeton, NJ, 08540} % Your address
%\address{123 Pleasant Lane \\ City, State 12345} % Your secondary addess (optional)
\address{Phone: 352-284-6720 \\ E-mail: carterjinhaoming@gmail.com} 
\address{LinkedIn: www.linkedin.com/in/haoming-jin/ \\ GitHub: https://github.com/carterjin} 

%\address{LinkedIn: www.linkedin.com/in/Haoming-Jin}  % Your phone number and email

\begin{document}

%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------
\vspace{-1em}
\begin{rSection}{Education}

{\bf University of Florida, Gainesville, FL, US} \hfill  {\em Aug. 2012 - May. 2020} 
\\ Ph.D. in Physics, Minor in Materials Science and Engineering \hfill GPA: 3.9/4.0
%\\ Ph.D. Minor in Materials Science and Engineering\\
\\{\bf Nanjing University, Nanjing, Jiangsu, China} \hfill  {\em Aug. 2008 - Jul. 2012} 
\\ Bachelor in Physics \hfill GPA: 3.5/4.0
\\{\bf Udacity}
\\ Data Scientist Nanodegree \hfill {\em May. 2020 - Present} 
\\ Data Analyst Nanodegree \hfill  {\em Mar. 2020}


\end{rSection}


%--------------------------------------------------------------------------------
%    Projects And Seminars
%-----------------------------------------------------------------------------------------------
\vspace{-9pt}
\begin{rSection}{SUMMARY OF SKILLS}\itemsep -3pt
\vspace{-3pt}
\textbf{Programming}: Python (3+ years), Matlab (5+ years), SQL (2 years), C++ (2 years)
\\
\textbf{Visualization}: matplotlib, seaborn, tableau
\\
\textbf{Technical}: Statistical Analysis (5+ years), Machine Learning (2 years), Data Wrangling
\end{rSection}

%----------------------------------------------------------------------------------------
%	TECHNICAL STRENGTHS SECTION
%----------------------------------------------------------------------------------------

%\begin{rSection}{Technical Strengths}
%
%\begin{tabular}{ @{} >{\bfseries}l @{\hspace{6ex}} l }
%Modeling and Analysis \ & AutoCad, Revit, StaadPro \\
%Software \& Tools & MS Office, Latex \\
%\end{tabular}
%
%\end{rSection}
\vspace{-9pt}
\begin{rSection}{Projects} 
%\vspace{-3pt}


\textbf{Price Evaluation with Machine Learning for Airbnb in San Francisco}\hfill {\em Apr - May. 2020}\\
\vspace{-15pt}
\begin{rSubsection}{}{}{}{}
\item Analyzed 12000+ Airbnb listing data in San Francisco using pandas in Jupyter Notebook (Python).
\item Cleaned and aggregated monthly updated files using pandas, incorporated the geological information to maps using the OpenStreetMap API and folium.
\item Used matplotlib and seaborn to visualize and present the findings. Evaluated pricing using scikit-learn and Keras with Linear Regression, Random Forest, and Neural Network, achieving 55.4\% $R^2$ score.
\end{rSubsection}

\vspace{-9pt}
\textbf{Ford GoBike System Data Exploration} \hfill {\em Apr. 2020}\\
\vspace{-15pt}
\begin{rSubsection}{}{}{}{}
\item Investigated 5.6 million Northern California bike rental records data with pandas.
\item Made exploratory data analysis on location, rental time, etc, with visualizations using matplotlib and tableau.
\item Concluded daily rental results were 76\% more on weekdays than weekends, and most of the rentals (70\%) occurred in the morning and afternoon rush hours, corresponding to commute traffic. 
\end{rSubsection}

\vspace{-9pt}
\textbf{Twitter WeRateDogs Data Wrangling with AI}\hfill {\em Feb. 2020}\\
\vspace{-15pt}
\begin{rSubsection}{}{}{}{}
\item Acquired 2000+ tweets data on dogs in WeRateDogs twitter archive using the twitter API, and parsed JSON objects to get retweet, favorite counts, etc.
\item Processed missing values, assessed data quality, and identified dog breeds using CNNs and transfer learning.
\item Summarized that the golden retriever was the most tweeted dog breed among 150 identified dog breeds, consisting of 7.4\% of all tweets, 45\% more than the second most tweeted dog breed.
\end{rSubsection}

\vspace{-9pt}
\textbf{Application Development on Github} \hfill {\em 2016 - 2020}\\
\vspace{-15pt}
\begin{rSubsection}{}{}{}{}
\item {Prime gap calculation with Rabin-Miller Algorithm}  \hspace{3pt} $\bullet$ {Chinese text conversion using pytesseract-OCR}
\item {Digit challenge using Shunting-yard algorithm} \hspace{29pt} $\bullet$ {Brute force zip password cracking with Python}
\end{rSubsection}

\end{rSection}


%	EXAMPLE SECTION
%----------------------------------------------------------------------------------------
\vspace{-12pt}
\begin{rSection}{EXPERIENCE} 
\textbf{University of Florida}\hfill {\em Aug. 2012 - May. 2020}\\
\textit{Graduate Researcher}
\begin{rSubsection}{}{}{}{}
%\item Study the prototypical electrical devices composing interfaces between 2D layered materials and resistive switching materials or semiconductors.
%\item  Initiate research topics, design experiment processes, participate in a collaboration project involving 13 experimental and theoretical groups in 3 research institutes.
\item Over five years experience of conducting data analysis and visualization on experiment output. Acquired critical parameters of novel prototypical electrical devices with linear regression and curve-fitting techniques using Matlab and Origin on over 15,000 sets of data. Used statistical models and A/B testing to test hypotheses. Presented findings on weekly group meetings and five global symposiums.
\end{rSubsection}
\end{rSection}

%\newpage

%----------------------------------------------------------------------------------------
% Extra-Curricular
%----------------------------------------------------------------------------------------
%\begin{rSection}{LEADERSHIP EXPERIENCE}
%\begin{rSubsection}{}{}{}{}
%\item Lead design, installation, and operation of the inert air glove box and 2D material dry transfer system, ion gun etching system, and thermal annealing system.
%\item Take charge of user training and instrument usage coordination of Quantum Design PPMS, SQUID system, and thermal evaporation deposition system. Maintain related cryogenic and vacuum systems. 
%\item Supervise safety regulations and hazardous waste management.
%\item Coordinate with engineers from different departments and companies to design and build custom electrical and mechanical equipment. Including parts for a custom integrated sputter/etch/measure system in high vacuum (SHIVA), with temperature and magnetic field altering abilities.
%\item Manage lab budgets, handle lab supplies, and equipment purchases with over ten companies.
%\item Instruct over 200 students on classical mechanics, electrodynamics and circuits, and advanced experiments such as cosmic muon detection, XRD, and optical tweezers, and receive an excellent rating.
%\end{rSubsection}
%\item Trained and disciplined in National Cadet Corps (NCC), IIT Kanpur for a year.
 %\item  Participated in Vijyoshi Camp 2012 organized at the Indian Institute of Science, Bangalore.
 %\item Won 2nd position in Kho-Kho in Intramurals conducted by Physical Education Section, IIT Kanpur.
 %\item Pursued French as a second language during secondary school from Grade 6 to Grade 10. I also participated in the French Song Competition and French G.K. Quiz in Class 10th. %

%\end{rSection}
\vspace{-12pt}
\begin{rSection}{Certifications}\itemsep -3pt
\vspace{-12pt}
\item Coursera: Machine Learning (with Matlab), Deep Learning (with Python), Advanced R Programming,\\ 
\hspace*{4.3em} Algorithm Specialization.
\item Udemy: The Complete SQL Bootcamp
\item Certified LabVIEW Associate Developer.
\item Second prize in 8th Nanjing University ACM programming competition.
\end{rSection}

%\vspace{-9pt}
%\begin{rSection}{Publications} \itemsep -3pt
%\vspace{-9pt}
%\item ``Improved memristive switching of graphite/Nb:SrTiO$_3$ interfaces by tuning Fermi levels and dielectric constants'', Xiaochen Zhu, \textbf{Haoming Jin}, Ang J. Li, Todd Schumann, and Arthur F. Hebard, J. Appl. Phys. B \textbf{124}, 152120 (2018).
%\end{rSection}

\end{document}
